### 2012-11-17 doc/rotation/abstract.tex
Added a rough introduction and fixed some typos

\begin{abstract}
This is the abstract for this article.
\end{abstract}

>>>>

\begin{abstract}

There has been a series of results recently on recovering hidden parameters
(inference) from probabilistic models using the method of moments. While this
problem is in general hard, use of certain spectral techniques like
eigen-decomposition have resulted in tractable inference using only the first
few moments (3-4) of the data. This article will survey these results, attempt
to describe the approach in general and discuss possible issues with their
generality.

\end{abstract}

### 2012-11-17 doc/rotation/perturbation-flow.tex
Added a rough introduction and fixed some typos

\tableref{tab:operators} lists the basic building blocks of these
algorithmic flow charts, along with absolute and relative errors of the
output {\em to first order}. The exact bounds and proofs for these can
be found in \appendixref{sec:perturbation-theory}.

@@

\begin{table}[htbp]
\floatconts
  {tab:rel-err}%
  {\caption{Relative Errors of Basic Operators}}%
  {\begin{tabular}{l | c | c c | l}
  \toprule
  \bfseries Operation & \bfseries Diagram & \bfseries Rel. Err. \\
  \midrule
  $A+B$         & \pdiagadd & $\frac{\|A\|\rerr{A} + \|B\|\rerr{B}}{\|A+B\|}$ \\
  $A*B$         & \pdiagmul & $\frac{\|A\|\|B\|}{\|AB\|} (\rerr{A} + \rerr{B})$ \\
  $A^{-1}$      & \pdiaginv & $\frac{\cnd{A}}{1 - \rerr{A}\cnd{A}} \rerr{A}$ \\
  $\lambda(A)$  & \pdiageig & $(2n-1) \cnd{A} \rerr{A}$ \\
  $\lambda(A_1, \cdots, A_{n})$  & \pdiageign & $O(n^3 \cnd{R}^2 \|\inv{R}\|^2 \inv{\gap{\lambda}}) \rerr{A}$ \\
  $\xi(A)$      & \pdiagevec & $n^3 \cnd{R} \|\inv{R}\| \gap{\lambda} \rerr{A}$ \\
  $\nu(A)$      & \pdiagsvec & $\rerr{A} + \rerr{B}$ \\
  $\hat{U}^T A \hat{V}$     & \pdiagrot & $\rerr{A}$ \\
  $W(A)$        & \pdiagwhite & \\
  $T[A,A,A]$    &             & \\
  \bottomrule
  \end{tabular}
  }
\end{table}

Describe the flow diagrams for each model and the computed complexity. (3hrs)

>>>>

\tableref{tab:operators} lists the basic building blocks of these
algorithmic flow charts, along with absolute errors of the output {\em
to first order}. The exact bounds and proofs for these can be found in
\appendixref{sec:perturbation-theory}.

@@

% \begin{table}[htbp]
% \floatconts
%   {tab:rel-err}%
%   {\caption{Relative Errors of Basic Operators}}%
%   {\begin{tabular}{l | c | c c | l}
%   \toprule
%   \bfseries Operation & \bfseries Diagram & \bfseries Rel. Err. \\
%   \midrule
%   $A+B$         & \pdiagadd & $\frac{\|A\|\rerr{A} + \|B\|\rerr{B}}{\|A+B\|}$ \\
%   $A*B$         & \pdiagmul & $\frac{\|A\|\|B\|}{\|AB\|} (\rerr{A} + \rerr{B})$ \\
%   $A^{-1}$      & \pdiaginv & $\frac{\cnd{A}}{1 - \rerr{A}\cnd{A}} \rerr{A}$ \\
%   $\lambda(A)$  & \pdiageig & $(2n-1) \cnd{A} \rerr{A}$ \\
%   $\lambda(A_1, \cdots, A_{n})$  & \pdiageign & $O(n^3 \cnd{R}^2 \|\inv{R}\|^2 \inv{\gap{\lambda}}) \rerr{A}$ \\
%   $\xi(A)$      & \pdiagevec & $n^3 \cnd{R} \|\inv{R}\| \gap{\lambda} \rerr{A}$ \\
%   $\nu(A)$      & \pdiagsvec & $\rerr{A} + \rerr{B}$ \\
%   $\hat{U}^T A \hat{V}$     & \pdiagrot & $\rerr{A}$ \\
%   $W(A)$        & \pdiagwhite & \\
%   $T[A,A,A]$    &             & \\
%   \bottomrule
%   \end{tabular}
%   }
% \end{table}
